---
title: "Compile a pdf version of adv-R"
output:
  pdf_document: default
  html_document: default
---
First of all, update the Rstudio & R and install the packages to the latest version in order to achieve a perfect result.

Install R bookdown package and R markdown package.
install.package("bookdown")
install.package("rmarkdown")

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Download the adv_r using git clone and follow the instruction given by the websites generates by Yihui Xie

I used the "git clone" from Hadley Wickham’s Github website to get the book folder (git clone https://github.com/hadley/adv-r.git) to my own personal laptop. Then open the adv-r.Rproj to start.
Then, go to the website (https://github.com/rstudio/bookdown-demo) to download the zip file for instruction. Follow the Yihui's steps and instructions on the website (https://bookdown.org/yihui/bookdown/get-started.html)

Then try the document "index.rmd" to find the packages that are still miising by click Build in the menu and follow with the build book button. Or using Knit -- Knit to pdf in menu part.

```{r cars}
summary(cars)
```

## Packages missing

1. install.packages('tinytex)
  tinytex::install_tinytex()
2. install devtools packages
3. devtools::install_github("hadley/sloop")
4. devtools::install_github("hadley/emo")

## Error massages after following all above steps

1. Error: LaTeX failed to compile _main.tex. See https://yihui.org/tinytex/r/#debugging for debugging tips. See _main.log for more info.
Solution: install the "tinytex" again and get the package update    tinytex::tlmgr_update()
## Result

Output created: _book/adv_r.pdf
[1] "/Users/guandi/Documents/stat5361/adv_r/_book/adv_r.pdf"

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
